The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-13 albatros_paper.tex
HCC editing section 1, added some references

\newcommand{\aap}{Astronomy and Astrophysics}
\newcommand{\aj}{Astronomical Journal}
\newcommand{\pasp}{Proceedings of the Astronomical Society of the Pacific}
\newcommand{\prd}{Physical Review D}
\newcommand{\apj}{Astrophysical Journal}
\newcommand{\aaps}{Astronomy and Astrophysics Supplements}

@@

\attention{Open task for any/all: fix references, make a proper bibtex file}

@@

Measurements of redshifted \SI{21}{\cm} emission of neutral hydrogen
across a wide range of radio frequencies have the potential to
elucidate the universe's history from the cosmic ``dark ages'' up to
the formation of large-scale structures (see,
e.g.,~\citep{ska_physics,2013PhRvD..87d3002L,2014ApJ...782...66P}.
The dark ages, which occurred after recombination and correspond to a
period when the universe was filled with neutral hydrogen, are
unexplored to date and represent one of the final observational
frontiers in cosmology.  This epoch contains a potential wealth of
cosmological information~\citep{loeb_zaldarriaga, 2019arXiv190710853C,
  2019arXiv190804296K}, but the required redshifted frequencies of
$\lesssim 30$~MHz are exceptionally difficult to observe.  The primary
experimental challenges include Galactic foreground emission,
ionospheric interference, and terrestrial radio-frequency interference
(RFI).

Very few experiments have measured the radio sky at $\lesssim 30$~MHz;
here, we highlight only four specific examples.  At the very lowest
frequencies, the state of the art among ground-based measurements
dates from the 1950s, when Reber and Ellis caught brief glimpses of
the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
space-based missions have also performed measurements at similarly low
frequency ranges; for example, the Radio Astronomy Explorer-2 operated
at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist mainly at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.  The first step
toward laying the groundwork for possible future cosmological
measurements is obtaining an improved map of Galactic foregrounds at
$\lesssim 30$~MHz.  Maps at these frequencies can additionally shed
new light on Galactic astrophysics, including cosmic ray structure
along the line of sight (\attention{more words here about synchrotron
  self-absorption}), \attention{words here about radio recombination
  lines}.  \attention{More words here about possible ionospheric
  studies.}

>>>>

\newcommand{\aap}{Astronomy and Astrophysics}
\newcommand{\aaps}{Astronomy and Astrophysics Supplements}
\newcommand{\aj}{Astronomical Journal}
\newcommand{\apj}{Astrophysical Journal}
\newcommand{\jgr}{Journal of Geophysical Research}
\newcommand{\pasa}{Publications of the Astronomical Society of Australia}
\newcommand{\pasp}{Proceedings of the Astronomical Society of the Pacific}
\newcommand{\prd}{Physical Review D}
\newcommand{\prl}{Physical Review Letters}

@@

\attention{Open task for any/all: fix references}

@@

Measurements of redshifted \SI{21}{\cm} emission of neutral hydrogen
across a wide range of radio frequencies have the potential to
elucidate the universe's history from the cosmic ``dark ages'' up to
the formation of large-scale structures (see,
e.g.,~\citep{2020PASA...37....2W,2013PhRvD..87d3002L,2014ApJ...782...66P}.
The dark ages, which occurred after recombination and correspond to a
period when the universe was filled with neutral hydrogen, are
unexplored to date and represent one of the final observational
frontiers in cosmology.  The number of independent modes that are
contained in the matter power spectrum in this epoch is orders of
magnitude greater than the corresponding number for cosmic microwave
background (CMB) measurements~\citep{2004PhRvL..92u1301L}.  Redshifted
21-cm measurements of the dark ages therefore hold the potential to
significantly improve cosmological parameter constraints over those
currently derived from the CMB; however, the required observational
frequencies of $\lesssim 30$~MHz are exceptionally difficult to
access.  The primary experimental challenges include Galactic
foreground emission, ionospheric interference, and terrestrial
radio-frequency interference (RFI).

Very few experiments have surveyed the radio sky at $\lesssim 30$~MHz,
and here, we highlight only four specific examples.  At the very
lowest frequencies, the state of the art among ground-based
measurements dates from the 1950s, when Reber and Ellis caught brief
glimpses of the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an
array of 192~dipoles~\citep{1956JGR....61....1R}.  A few space-based
missions have also performed measurements at similarly low frequency
ranges; for example, the Radio Astronomy Explorer-2 operated at
\SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist mainly at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.  The first step
toward laying the groundwork for possible measurements of the dark
ages is obtaining an improved map of Galactic foregrounds at $\lesssim
30$~MHz.  In addition to serving as a stepping stone for future
cosmological constraints from the dark ages, maps at these frequencies
can also shed new light on Galactic astrophysics.  Above $\sim30$~MHz,
synchrotron emission from the Galaxy follows a power law with a
frequency dependence of $\nu^{-5/2}$.  At lower frequencies,
synchrotron self-absorption becomes non-negligible, and the spectrum
transitions to $\nu^{5/3}$ dependence.  Since self-absorption causes
the optical depth along the line of sight to depend on frequency,
observations at $\lesssim 30$~MHz have the potential to probe the
three-dimensional cosmic ray structure of the
Galaxy~\citep{2002ApJ...575..217P}.

\attention{Words here about radio recombination lines.}
\attention{More words here about possible ionospheric studies.}

% Words here about space-based concepts, and more words about doing
% what we can from the ground first
